Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-07 Report/ReportFHE.tex
rien

\maketitle
\begin{abstract}
We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... \\\\\\\\\\\\\\\\\\\\\\\\\\
\end{abstract}

@@

(Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed.) \\\\\\
A partially homomorphic encryption allows certain operations on ciphertexts such as addition or multiplication which implies a known operation on plaintext like RSA Encryption
\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] \\
then Gentry proved that there is a fully homomorphic encryption which allows both addition and multiplication on encrypted bits: 
\[\texttt{FHE}(m1) + \texttt{FHE} (m2) = \texttt{FHE}(m1+m2) \] 
\[\texttt{FHE}(m1) \times \texttt{FHE} (m2) = \texttt{FHE}(m1 \times m2) ;\ \ \ m1, m2 \in \left\{ 0, 1 \right\}\] 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\section{Gentry's fully homomorphic scheme}
 FHE\\\\\\\
\subsection{The Framework}
Overview of the algorithm and its complexity. 
 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

@@

\[r_1= a_1.b_1 ; c_{1,1}=0\] 
\[(r_2,c_{1,2})=\texttt{add}(a_2.b_1 ,a_1.b_2 ,c_{1,1}  ) \] 
\[(r_3,c_{2,3})=\texttt{add}(a_1.b_3,\texttt{add}( a_3.b_1, a_2.b_2 , c_{1,2} ))   \] 
 \[ \vdots    \] 
\[ (r_{n-1},c_{n-1,n-1})= ...    \] 
\[(r_{n},c_{n,n})=\texttt{add}(a_1.b_n, ...)      \] 
\[  (r_{n+1},c_{n+1,n+1})= ..   \] 
\[  \vdots      \] 
\[  (r_{2n-1},c_{2n-1,2n-1})=     \] 
\[ (r_{2n},c_{2n,2n})=  \texttt{add}(a_n.b_n, c_{2n,2n-1})    \]
So it has $O(n^{2})$ complexity. In addition to that there is the cost of key generation, encryption and decryption, and there is also the recrypt algorithm called after each addition or multiplication. On the other hand the RSA-Encryption is encrypted much more easier but has a similar cost on multiplication of n-bits integer.
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

>>>>

\maketitle
\tableofcontents

\begin{abstract}
We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... \\\\\\\\\\\\\\\\\\\\\\\\\\
\end{abstract}

@@

(Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed.) \\\\\\
A partially homomorphic encryption allows certain operations on ciphertexts such as addition or multiplication which implies a known operation on plaintext like RSA Encryption
\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] \\
then Gentry proved that there is a fully homomorphic encryption which allows both addition and multiplication on encrypted bits: 
\[\texttt{FHE}(m1) + \texttt{FHE} (m2) = \texttt{FHE}(m1+m2) \] 
\[\texttt{FHE}(m1) \times \texttt{FHE} (m2) = \texttt{FHE}(m1 \times m2) ;\ \ \ m1, m2 \in \left\{ 0, 1 \right\}\] 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\section{Gentry's fully homomorphic scheme}
 FHE\\\\\\\
\subsection{The Framework}
(Overview of the algorithm and its complexity. )
In this study we use two variants of fully homomorphic encryption: 
\begin{itemize}
\item Smart-Vercauteren implementation

\item Gentry-Halevi-Smart implementation

\end{itemize}

 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

@@

\[r_1= a_1.b_1 ; c_{1,1}=0\] 
\[(r_2,c_{1,2})=\texttt{add}(a_2.b_1 ,a_1.b_2 ,c_{1,1}  ) \] 
\[(r_3,c_{2,3})=\texttt{add}(a_1.b_3,\texttt{add}( a_3.b_1, a_2.b_2 , c_{1,2} ))   \] 
 \[ \vdots    \] 
\[ (r_{n-1},c_{n-1,n-1})= ...    \] 
\[(r_{n},c_{n,n})=\texttt{add}(a_1.b_n, ...)      \] 
\[  (r_{n+1},c_{n+1,n+1})= ..   \] 
\[  \vdots      \] 
\[  (r_{2n-1},c_{2n-1,2n-1})=     \] 
\[ (r_{2n},c_{2n,2n})=  \texttt{add}(a_n.b_n, c_{2n,2n-1})    \]
So it has $O(n^{2})$ complexity. In addition to that there is the cost of key generation, encryption and decryption, and there is also the recrypt algorithm called after each addition or multiplication. On the other hand the RSA-Encryption is much more easier and has a O(1) complexity for the multiplication of n-bits integer.
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
